Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-11-03 supp/index.Rmd
<edit index>

```{r figmap, fig.cap="Location of Millsap Cache, Jowell Farm, and other Caddo sites mentioned in the text. Elliptical bifaces have been found in every major river basin in the ancestral Caddo area (dashed/white)."}

@@

The pattern that emerges is one of differential retouch _intensity_, where the isometric reduction strategies of one group (Millsap Cache) may correlate with differing retouch practices that articulate with locally abundant raw material (Kay County flint). This stands in contrast to the comparatively minimal retouch intensity of another group (Jowell Farm) where local raw material was of an insufficient size, yielding a situation where it was necessary to import raw material from an extralocal source in central Texas (Edwards chert).

>>>>

```{r figmap, fig.cap="Location of Millsap Cache, Jowell Farm, and other Caddo sites mentioned in the text. Elliptical bifaces have been found in all but one major drainage basin in the ancestral Caddo area (dashed/white)."}

@@

The pattern that emerges is one of differential retouch _intensity_, where the isometric reduction strategies of one group (Millsap Cache) articulates with a different reduction practice thought to be associated with locally abundant raw material (Kay County flint). This stands in contrast to the comparatively minimal retouch intensity of another group (Jowell Farm) where local raw material was of poor quality and insufficient size, yielding a situation where it was necessary to import raw material from an extralocal source (Edwards chert).
